---
title: "Wild Data"
format: html
editor: Source
error: FALSE
warning: FALSE


library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
---

-   What does each column contain?

    Information about a tag on an invertebrate and information about the invertebrate

-   What are the units of each?

    mostly numbers, sizes in millimeters and weight in grams

-   What is the study overall about?

```         
Tags on individual invertabrates
```
Read in the data using read_csv() with here(), store as mack_verts

Look at what you’ve read in (e.g. with view())
```{r}
mack_verts <- read_csv(here("data/AS00601_v9.csv"))
view(mack_verts)
mack_verts <- janitor::clean_names(mack_verts)
```
Update the variable names in mack_verts to lower snake case

In a new code chunk, practice accessing individual pieces of the data frame (there is no real functionality to this right now, but just to reinforce stuff we learned in our interactive session):

Store the 5th value in column “WEIGHT” as mc_wt_5. Check by looking at your data frame to confirm.
Store the 8th - 20th value in the “LENGTH1” column as mc_length_8_20. Check by looking at your data frame to confirm.
Store everything in column SAMPLEDATE as a vector called mc_dates
```{r}
mc_wt_5 <- mack_verts[[5, 15]]
mc_wt_5

mc_length_8_20 <- mack_verts[8:20, "length1"]
mc_length_8_20

mc_dates <- mack_verts["sampledate"]
mc_dates

mc_salamanders <- dplyr::filter(.data = mack_verts, species == "DITE")
mc_salamanders

```

```{r}
salamanders_size <- ggplot(data = mc_salamanders, aes(x = length1, y = weight)) +
geom_point(size = 2, alpha = 0.8, color = "blue" ) +
  labs(title = "Size of DITE Pacific Giant Salamanders", 
       subtitle = "Good Graph Lucian", 
       caption = "Source from Mack Creek salamander & cutthroat trout data", 
       x = "snout-vent length in millimeters", 
       y = "grams") +
  theme_minimal()
  
salamanders_size

ggsave(here::here("figs", "salamanders_size.png"), height = 3, width = 4)
  
```

```{r}
mc_trout <- dplyr::filter(.data = mack_verts, species == "ONCL")
mc_trout

cutthroat_size <- ggplot(data = mc_trout, aes(x = length1, y = weight, colour = reach, facet_wrap(~reach))) +
geom_point(size = 2, alpha = 0.8, color = "purple") +
  labs(title = "Size of ONCL Cutthroat Trout", 
       subtitle = "Good Graph Lucian", 
       caption = "Source from Mack Creek salamander & Cutthroat Trout data", 
       x = "length in millimeters", 
       y = "weight in grams") +
  theme_minimal() +
  scale_color_manual()
  
cutthroat_size

ggsave(here::here("figs", "cutthroat_size.png"), height = 3, width = 4)
  
```

